Timeliness of security updates for Android

### 2014-08-27 securityupdates.tex
Talk about the gap in vulnerability discovery

>>>>

This data shows a large gap in the middle where we do not know of any discoveries of root equivalent vulnerabilities affecting all of Android.
The cause of this quiet period is unclear, perhaps from Figure~\ref{fig:proportioninsecure} the reason was that since most devices were exposed to known vulnerabilities there was no point in looking for new ones?
Or that manufacturers made it easier to install custom versions of Android, reducing the need for users to root their devices?
Or that manufacturer specific vulnerabilities proved to be easier to find and so people looking for vulnerabilities adjusted their focus?
